---
name: Shaza
surname: Mumtaz
position: "MBA Graduate | Hospitality Management Professional"
email: "ssmumtaz@cpp.edu"
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::latexcv:
    theme: classic
header-includes:
   - \usepackage{enumitem}
   - \setlist[itemize]{nosep, left=0pt}
   - \setlist[enumerate]{nosep, left=0pt}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

if (!requireNamespace(c("tinytex","vitae","tibble"), quietly = TRUE)) {
  install.packages(c("tinytex","vitae","tibble"))
}

if (Sys.which("pdflatex") == "" && !tinytex::is_tinytex()) {                    
  message("► TinyTeX not found – installing")
  tinytex::install_tinytex()        
} else {
  message("✓ LaTeX present – no installation needed.")
}

library(vitae)
library(tibble)
```

# Professional Summary

Results-oriented MBA graduate with expertise in operations management, marketing, and financial analysis, passionate about advancing in the hospitality industry. Proficient in leveraging data-driven strategies and business analytics to optimize operational efficiency, enhance customer satisfaction, and drive revenue growth. Skilled in analytical tools and strategic planning to support hospitality business objectives.

# Technical Skills

- **Analytical Tools**: Excel, Python, Google Analytics, Canva  
- **Business Skills**: Operations Management, Marketing Strategy, Financial Modeling, Data Analysis, Process Optimization  
- **Hospitality Skills**: Customer Service Excellence, Workflow Coordination, Revenue Analysis, Marketing Campaign Development

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ College, ~ Institution,
  "Master of Business Administration (General)", "2021 – 2023", "College of Business Administration", "Cal Poly Pomona"
) %>%
  detailed_entries(Degree, Year, College, Institution)
```

# Work Experience

```{r}
tribble(
  ~ Years, ~ Company, ~ Duties, ~ Title,

  "June 2022 – August 2022", "Hospitality Solutions Inc.",
  list(
    "Analyzed operational workflows for hospitality clients, identifying inefficiencies in service delivery processes.",
    "Developed process maps using Excel, improving operational efficiency by 15%.",
    "Collaborated with cross-functional teams to implement streamlined procedures.",
    "Used data analytics to support recommendations, enhancing service quality.",
    "Presented findings to stakeholders, driving adoption of optimized workflows."
  ),
  "Operations Analyst Intern",

  "January 2023 – May 2023", "Hospitality Marketing Group",
  list(
    "Designed marketing campaigns for hospitality businesses, increasing brand visibility by 20%.",
    "Created promotional assets using Canva, tailored to target customer demographics.",
    "Analyzed campaign performance with Google Analytics, optimizing digital marketing strategies.",
    "Supported training on customer service best practices for hospitality staff.",
    "Implemented data-driven marketing tactics, boosting customer engagement."
  ),
  "Marketing Assistant"

) %>%
  detailed_entries(
    what = Title,
    when = Years,
    with = Company,
    why = Duties
  )
```